---
title: "Supplementary File 7: generalised additive models for offspring wet weight"
header includes:
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
opts_chunk$set(echo = F)
```

Generalised additive models were fitted using cubic regression splines. Maternal age was included as an explanatory variable and individual mother included as a random effect.
Akaike's information criteria corrected for small sample size (AICc) was used to decide the most parsimonious number of knots (Tables 1 to 3). For each treatment, the most parsimonious model fit was then compared with model fits assuming a quadratic relationship between maternal age and offspring wet weight.

```{r }
controlGAMTable <- readRDS(file = "GAMfitsctrl.rds")
kable(controlGAMTable,caption="Control treatment: AICc by number of knots") %>%
  kable_styling(latex_options = "hold_position")
  
```


```{r }
mateGAMTable <- readRDS(file = "GAMfitsmate.rds")
kable(mateGAMTable,caption="Mating delay treatment: AICc by number of knots") %>%
  kable_styling(latex_options = "hold_position")
  
```


```{r }
nutsGAMTable <- readRDS(file = "GAMfitsnuts.rds")
kable(nutsGAMTable,caption="Nutritional stress treatment: AICc by number of knots") %>%
  kable_styling(latex_options = "hold_position")
  
```


\newpage
Figure 1. Comparison of generalised additive (GAM) and quadratic model fits for the effect of maternal age on offspring wet weight. Black dashed lines - quadratic fit, solid lines - GAM fits and standard error.

```{r }
plotMods <- readRDS(file = "FigSuppGAMWeight.rds")
plotMods
```


